Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus

### 2023-09-05 manuscript_thev_transcriptome.Rmd
fixed E4 transcript positioning in plot

>>>>

```{r region-by-region_e1_figure}
set_flextable_defaults(font.size = 7)
flextable(reg_e1_brkdown) %>% theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed",
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::font(part = "all", fontname = "Avenir") %>%
  flextable::set_header_labels(start = "Start", end = "End",
                               splice_site = "Splice Site", region = "Region",
                               strand = "Strand", trxpt_id = "Transcript ID",
                               coding_potential = "Protein Coding Potential",
                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
                               "72hpi" = "72h.p.i") %>%
  flextable::width(., width = 0.5) %>%
  flextable::align(align = "center", part = "all") %>%
  add_header_row(., values = c("", "Splice Junction", "", "", "Junction Reads", ""),
                 colwidths = c(1, 4, 1, 1, 4, 1)) %>%
  flextable::vline(j = c(1, 5, 7, 11), border = fp_border_default(color = "grey",
                                                                  width = 1.5))  %>%
  flextable::width(., j = ~ coding_potential, width = 1)
```
